\documentclass[11pt]{article}

% \usepackage[UTF8]{ctex} % for Chinese 

\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=red,citecolor=black]{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{floatrow}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{natbibspacing}
\usepackage[toc,page]{appendix}
\usepackage{makecell}
\usepackage{amsfonts}
 \usepackage{amsmath}

\title{Insect-symbiont gene expression in the midgut bacteriocytes of a blood-sucking parasite}
\author{}
\date{}

\linespread{1.5}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}

\begin{document}
  \maketitle

  \linenumbers
Sheep ked \textit{Melophagus ovinus} is a species of wingless, blood-sucking insect that is permanently associated with vertebrate host and transmitted via host interactions. 
Its primary bacterial symbiont \textit{Arsenophonus melophagi} lives intracellularly in bacteriocytes that assemble into special structure (bacteriome) in midgut. 

\newline

Sheep ked interacts with its symbiont nutritionally. 
Transcription analysis shows symbiont high expression of a pathway that converts proline to L-glutamate through the PutA enzyme (EC 1.5.5.2/1.2.1.88) and its subsequent conversion to D -glutamate by the MurI enzyme (EC 5.1.1.3). 
Proline is almost always the most common amino acid in insect hemolymph (Arrese and Soulages 2010). 
In insects, proline is generally reserved for energy-demanding activity such as flight. 
In wingless sheep ked, proline storage might be used for bacterial symbiont for energy metabolism and peptidoglycan synthesis. 
However, the symbiont expression of B-vitamin synthesis is low, except that of lipoic acid. 
It is possible that B vitamins are not essential for sheep ked, or are only needed during particular life stage. 
It is also possible that sheep ked does not rely on symbiont for B vitamins.

\newline

Symbiont \textit{Arsenophonus} might be dependent on host for metal ions. 
High expression of zinc transporters in bacteriocytes and symbionts, together with low expression of zinc protease in bacteriocytes, indicate that symbiont \textit{Arsenophonus} is demanding on zinc. 
Symbiont zinc-dependent proteins might be protease, or a putative metalo-beta-lactamase. 
Beta-lactamases are enzymes that provide bacteria with resistance to beta-lactam antibiotics such as penicillin, ampicillin. 
Metalo-beta-lactamases in particular are well-known for their resistance to a broad spectrum of beta-lactam antibiotics and beta-lactamase inhibitors (Bradford 2001; Drawz and Bonomo 2010). 
The sheep from which sheep keds are collected are often treated with beta-lactam antibiotics. 
Besides, ferritin is highly expressed among whole gut, and transferrin is down-regulated in bacteriocytes. 
Ferritin sequesters iron from a blood meal and blocks iron ions intracellularly, while transferrin mediates transport of iron through blood plasma. 
Transferrin can also act as an antimicrobial protein sequestering iron from pathogens (Yoshiga et al.
2001). 
Down-regulation of transferrin in bacteriome might be a sort of immune privilege.

\newline

There is potential immune compromise in sheep kep bacteriome. 
Immune response genes such as attacin (antimicrobial peptide) and two lysozymes, are down-regulated in bacteriocytes. 
PGRP-LB, an amidase that degrades peptidoglycan to inhibit immune responses, is highly expressed along whole gut, while GNBP, a pattern recognition receptor, is lowly expressed along gut. 
Furthermore, sheep ked lacks peritrophic matrix, a physical barrier to protect against pathogens. 
It is consist with the lack of chitin synthesis in sheep ked gut.

\end{document}