\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=red,citecolor=black]{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{floatrow}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{natbibspacing}
\usepackage[toc,page]{appendix}
\usepackage{makecell}
\usepackage{amsfonts}

\title{Measuring and Comparing Biodiversity}
\date{}

\linespread{1.5}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}

\begin{document}

  \maketitle

  \linenumbers

\section{Diversity of species, phylogeny and function}
For an assemblage of individuals, its diversity can be measured in ways different in incorporation of species difference. 
In species diversity, all species are assumed to be equally distinct. 
In phylogenetic diversity, evolutionary or phylogenetic differences, \textit{e.g.} taxonomic classification and well-supported phylogenetic tree, is taken into consideration. 
All else being equal, an assemblage of closely related species is less diverse in terms of phylogeny than an assemblage composed of highly divergent species. 
In functional diversity, species are described by a set of traits and species difference can be measured by dissimilarities of trait profiles. 
There are three main approach to functional diversity measures: distance based, dendrogram based and trait-value based.

\section{Classic measures of species diversity}
\label{SpeciesRichness}
Species richness is a simple count of number of species present in an assemblage. 
It is an intuitive and frequently used diversity index and is a key metric in conservation biology. 
However, it does not incorporate information about species abundances and is difficult to estimate accurately from small samples. 

\newline

Shannon index is another measure of diversity, defined as 
\begin{equation}
    H_{Sh} = -\sum\limits_{i=1}^{S}p_i \ln p_i
    \label{ShannonIndex}
\end{equation}
where $S$ is species richness and $p_i$ is the relative abundance of $i$th species.

\newline

Gini-Simpson index is another popular measure of diversity, defined as 
\begin{equation}
    H_{GS}=1-\sum\limits_{i=1}^{S}p_i^2
    \label{GiniSimpsonIndex}
\end{equation}
It gives the probability that two randomly drawn individuals belong to different species.

\newline

Species richness, Shannon index and Gini-Simpson index can be united into a family of generalized indexes, parametrized by a variable $q \ge 0$. 
The generalized index is defined as 
\begin{equation}
    ^{q}H = \frac{1-\sum\limits_{i=1}^{S} p_i^q}{q-1}
    \label{GeneralizedIndex}
\end{equation}
Thus,
\begin{equation}
    ^{0}H = S-1
\end{equation}
\begin{equation}
    ^{1}H = \lim\limits_{q\rightarrow 1}{^{q}H} = H_{Sh}
\end{equation}
\begin{equation}
    ^{2}H = H_{GS}
\end{equation}

\section{Classic measures of phylogenetic diversity}
\label{FaithPD}
Faith's phylogenetic diversity (PD) (Faith 1992) is a widely used measure of phylogenetic diversity. 
It is defined as the sum of all branch lengths of a phylogenetic tree connecting all species present in an assemblage. 
Like species richness, Faith's PD does not incorporate information on species abundance.

\newline

Rao's quadratic entropy (Rao 1982) incorporates both phylogeny and species abundances, defined as 
\begin{equation}
    Q = \sum\limits_{i=1}^{S}\sum\limits_{i=1}^{S} d_{ij}p_{i}p_{j}
    \label{RaoPD}
\end{equation}
where $d_{ij}$ is the phylogenetic distance between $i$th and $j$th species. 

\newline

Allen \textit{et al} (2009) proposed another measure of phylogenetic measure: 
\begin{equation}
    H_p = -\sum\limits_{i} L_ia_i \ln a_i
    \label{AllenPD}
\end{equation}
where $L_i$ is the length of branch $i$, $a_i$ is the summed relative abundance of all species descended from branch $i$.

\newline

For an ultrametric tree in which all branch tips are the same distance (denote by depth $T$) to the root, Faith's PD, Rao's $Q$ and $H_p$ of Allen \textit{et al} can be generalized as (Pavoine \textit{et al} 2009)
\begin{equation}
    ^{q}I = \frac{T-\sum\limits_{i}L_ia_i^q}{q-1}
    \label{GeneralizedPD}
\end{equation}
Thus,
\begin{equation}
    ^{0}I = \sum\limits_{i}L_i - T
\end{equation}
\begin{equation}
    ^{1}I = \lim_{q\rightarrow 1} {^{q}I} = -\sum\limits_{i}L_ia_i\ln a_i
\end{equation}
\begin{equation}
    ^{2}I = T-\sum\limits_{i}L_i a_i^2
\end{equation}

\section{Classic measures of functional diversity (distance-based)}
Functional attribute diversity (FAD) (Walker \textit{et al} 1999) is the sum of the pairwise distances between species: 
\begin{equation}
    FAD = \sum\limits_{i=1}^{S}\sum\limits_{j=1}^{S}d_{ij}
    \label{FAD}
\end{equation}
where $d_{ij}$ is the functional distance of species $i$ and $j$.

\newline

Rao's $Q$ (Equation \ref{RaoPD}) can be used as a measure of functional diversity, replacing $d_{ij}$ by functional distance. 
Guiasu (2011, 2012) proposed a weighted Gini-Simpson index for pairs of species as follows:
\begin{equation}
    GS_D = \sum\limits_{i=1}^{S}\sum\limits_{j=1}^{S}d_{ij}p_ip_j = Q-\sum\limits_{i=1}^{S}\sum\limits_{j=1}^{S}d_{ij}(p_ip_j)^2
    \label{Guiasu}
\end{equation}

\newline

Ricota & Szeidl (2009) and de Bello \textit{et al} (2010) transformed Rao's $Q$ for functional diversity to the effective number of species with a maximum species pairwise distance $d_{max}$. 
It is the theoretical species richness of a perfectly even assemblage with the same Rao's $Q$ as the original assemblage:
\begin{equation}
    Q_e = \frac{1}{1-Q/d_{max}}
    \label{EffectiveRichnessQ}
\end{equation}

\section{Measure diversity by Hill numbers}
% Consider an assemblage of $S$ species with relative abundance $\{p_1,p_2.p_3,\dots,p_S\}, \sum\limits_{i=1}^{S}p_i=1$. All species are connected by a phylogenetic tree and a matrix of pairwise distance between species based on functional traits. 
Measures of species diversity, phylogenetic diversity and functional diversity can be incorporated into a unified framework based on Hill numbers (Chao and Chiu \textit{et al}, 2014)
Denote by $C$ an assemblage of entities (species or phylogenetic tree branch segments or species pairs), and by $u$ elements in $C$. 
For each $u$, denote by $v_u$ its attribute value and by $a_u$ its weight (\textit{e.g.} biomass, cover area, abundance). 
The weighted mean attribute value is
\begin{equation}
    \bar{V} = \sum\limits_{u\in C}a_uv_u
\end{equation}
The Hill number of order $q$ is defined as 
\begin{equation}
    ^{q}AD(\bar{V}) = 
    [\sum\limits_{u\in C} v_u \times (\frac{a_u}{\bar{V}})^q]^{\frac{1}{1-q}} = [\sum\limits_{u\in C} v_u \times (\frac{a_u}{\sum\limits_{u\in C}a_uv_u})^q]^{\frac{1}{1-q}}
\end{equation}
AD is short for attribute diversity. 
Further, 
\begin{equation}
    ^{0}AD(\bar{V}) = \sum\limits_{u\in C}v_u
\end{equation}
\begin{equation}
    ^{1}AD(\bar{V}) = \lim\limits_{q\rightarrow 1}{^{1}AD(\bar{V})} = exp\{-\sum\limits_{u\in C}v_u\frac{a_u}{\bar{V}}\ln\frac{a_u}{\bar{V}}\} 
\end{equation}
\begin{equation}
    ^{2}AD(\bar{V}) = \frac{1}{\sum\limits_{u\in C}v_u (\frac{a_u}{\bar{V}})^2}
\end{equation}

\newline



\newpage
\textbf{References} %APA
\newline
[1] Chao, A. , Chiu, C. H. , & Jost, L. . (2014). Unifying species diversity, phylogenetic diversity, functional diversity, and related similarity and differentiation measures through hill numbers. Annual Review of Ecology Evolution & Systematics, 45(1), 297-324.
\end{document}